Synthesizing Symmetric Lenses

### 2019-02-28 papers/SymmetricLenses/main.tex
Couple more comments

\begin{figure}
  \includegraphics{generated-graphs/times}
  \vspace{-4ex}
  \caption{Number of benchmarks that can be solved by a given algorithm in a
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \SSNCOpt{} is the symmetric synthesis algorithm without using a library of
    existing lenses. The symmetric synthesis algorithm is able to complete all
    benchmarks in under 30 seconds elapsed total time. Without compositional
    synthesis it is able to complete 26. Each benchmark specification includes
    source and target (potentially annotated) regular expressions, and between
    one and three sufficient examples.}
  \label{fig:times}
\end{figure}

@@

% begin conclusion
\section{Conclusion}
\label{sec:conc}
We have developed a synthesis algorithm for synthesizing synchronization
functions between data formats that may not be in bijective correspondence. More
specifically, we identify a subset of symmetric lenses, simple symmetric lenses,
develop new combinators for them, and show how to synthesize them from regular
expression specifications. In order to guide the search for ``likely'' lenses,
we introduce new search principles based on information theory. Based on these
principles, we designed, implemented, and evaluated a new tool for lens
synthesis.

>>>>

\begin{figure}
  \includegraphics{generated-graphs/times}
  \vspace{-4ex}
  \caption{\bcp{What are the little tick marks on the top of the figure?
      And why do we need a line for ``benchmark count''?}Number of
    benchmarks that can be solved by a given algorithm in a 
    given amount of time. \SSOpt{} is the full symmetric synthesis algorithm.
    \SSNCOpt{} is the symmetric synthesis algorithm without using a library of
    existing lenses. The symmetric synthesis algorithm is able to complete all
    benchmarks in under 30 seconds elapsed total time. Without compositional
    synthesis it is able to complete 26. Each benchmark specification includes
    source and target (potentially annotated) regular expressions, and between
    one and three sufficient examples.}
  \label{fig:times}
\end{figure}

@@

% begin conclusion
\section{Conclusion}
\label{sec:conc}
We described a synthesis algorithm for synthesizing synchronization
functions between data formats that may not be in bijective correspondence.
We identified a subset of symmetric lenses, simple symmetric lenses, 
develop new combinators for them, and show how to synthesize them from regular
expression specifications. In order to guide the search for ``likely'' lenses,
we introduce new search principles based on information theory. Based on these
principles, we designed, implemented, and evaluated a new tool for lens
synthesis.

\bcp{Future work??????????????}
